A pipeline to analyse time-course gene expression data

### 2020-07-20 scripts/manuscript.Rmd
manuscript runs on my computer

```{r averageSilhouetteMethod, fig.width=6, fig.height=4, fig.cap="Plot of silhouette values as a function of k"}
# function to compute average silhouette for k clusters
average_silhouette = function(labels, y) {
    silhouette_results = silhouette(unlist(labels[1]), dist(y))
    return(mean(silhouette_results[, 3]))
}

@@

Using the bootstrapping strategy, we sample with replacement a sample of the
same size as our original clustering (i.e. `r dim(y)[1]` genes):

>>>>

```{r averageSilhouetteMethod, fig.width=6, fig.height=4, fig.cap="Plot of silhouette values as a function of k"}
# function to compute average silhouette for k clusters
average_silhouette = function(labels, y) {
    silhouette_results = silhouette(unlist(labels[1]),dist(y))
    return(mean(silhouette_results[, 3]))
}

@@

Using the bootstrapping strategy, we sample with replacement a sample of the
same size as our original clustering (i.e. `r dim(de_moanin_model)[1]` genes):
